\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-05-07 sections/results.tex
Change: Update the tables and figures for draft v2

  To compare the representative sequences generated by these methods we employ both the weighted~\cite{Lozupone2007} (Figure~\ref{fig:figure3}A) and unweighted UniFrac method~\cite{Lozupone2005} (Figure~\ref{fig:figure3}B).
  In both the comparisons, we set a count threshold of 10, such that if the count of the representative sequences in a particular sample is less than the threshold, it is omitted from the analysis.
  The values shown in the figures correspond to the mean UniFrac values across all samples in the study.
  The weighted UniFrac distance metric takes into account the counts of the representative sequences, whereas the unweighted UniFrac distance metric does not and hence gives equal weights to each sequence.
  From Figure~\ref{fig:figure3}A one can see that the representative sequences generated by the different methods, with the exception of Deblur, are similar to each other when weighted by their abundance.
  Figure~\ref{fig:figure3}B on the other hand shows an increase in dissimilarity between each pair of methods suggesting that the methods might differ in the assignment of sequences lower in abundance.
  In order to verify this claim, for each of these methods we filtered out only the top 1000 representative sequences and recalculated the distance metrics for each method (Figure \ref{fig:figureS3}).
  We observe that the both the weighted and unweighted UniFrac distances are increased implying that the top representative sequences generated by the different methods are not as similar to each other.
  % TODO: Can we make this conclusion?
  This leads us to conclude that the representative sequences in the middle range of the abundance distribution are those that must be the most similar between the methods.

@@

  The systematic analyses performed in the previous sections clearly show that the choice of tools and parameters can have a big impact on the final co-occurrence network.
  For some of these choices (e.g. \ac{dada2} vs. Deblur), there is no clear metric to establish the best protocol.
  For other choices, the mock communities and synthetic data provide an opportunity to select the combinations of tools that yield more accurate and robust results.
  Despite this partial degree of assessment, we wish to suggest a combination of tools and parameters that produce networks that are derived from the combination of tools which performed best on the mock communities, and displayed the highest robustness to switching to alternative methods.
  These tools and parameters are chosen as the defaults for the pipeline and are given in Table~\ref{tab:default_options}.

@@

  % TODO: Say that this shows how important the consensus network is in the whole pipeline
  The low L1 distances show us that not only does the consensus help reconcile the variability in the edges due to multiple network inference algorithms, it also helps reconcile the variability to the other steps of the pipeline as well.
  This result is different from that observed in Figure~\ref{fig:figure2} since in this particular analysis all the steps other than the \ac{ni} step have the consensus algorithm applied to them, which drastically reduces the edges in the graph that have lower probabilities.
  This reinforces the importance of the consensus network in increasing the robustness of the inferred networks to different processing methods.
  Figure~\ref{fig:figure7}C shows the co-occurrence networks inferred for the healthy subjects (control) and autistic subjects in the fecal microbiome transplant study~\cite{Kang2017}.
  These consensus networks were generated using the default tools and parameters from Table~\ref{tab:default_options}.

>>>>

  To compare the representative sequences generated by these methods we employ both the weighted~\cite{Lozupone2007} (Figure~\ref{fig:figure3}A) and unweighted UniFrac method~\cite{Lozupone2005} (Figure~\ref{fig:figure3}B).
  In both the comparisons, we set a count threshold of 10, such that if the count of the representative sequences in a particular sample is less than the threshold, it is omitted from the analysis.
  The values shown in the figures correspond to the mean UniFrac values across all samples in the study.
  The weighted UniFrac distance metric takes into account the counts of the representative sequences, whereas the unweighted UniFrac distance metric does not and hence gives equal weights to each sequence.
  From Figure~\ref{fig:figure3}A one can see that the representative sequences generated by the different methods, with the exception of Deblur, are similar to each other when weighted by their abundance.
  Figure~\ref{fig:figure3}B on the other hand shows an increase in dissimilarity between each pair of methods suggesting that the methods might differ in the assignment of sequences lower in abundance.
  In order to verify this claim, for each of these methods we filtered out only the top 1000 representative sequences and recalculated the distance metrics for each method (Figure \ref{fig:figure_s3}).
  We observe that the both the weighted and unweighted UniFrac distances are increased implying that the top representative sequences generated by the different methods are not as similar to each other.
  % TODO: Can we make this conclusion?
  This leads us to conclude that the representative sequences in the middle range of the abundance distribution are those that must be the most similar between the methods.

@@

  The systematic analyses performed in the previous sections clearly show that the choice of tools and parameters can have a big impact on the final co-occurrence network.
  For some of these choices (e.g. \ac{dada2} vs. Deblur), there is no clear metric to establish the best protocol.
  For other choices, the mock communities and synthetic data provide an opportunity to select the combinations of tools that yield more accurate and robust results.
  Despite this partial degree of assessment, we wish to suggest a combination of tools and parameters that produce networks that are derived from the combination of tools which performed best on the mock communities, and displayed the highest robustness to switching to alternative methods.
  These tools and parameters are chosen as the defaults for the pipeline and are given in Table~\ref{tab:micone_tools}.

@@

  % TODO: Say that this shows how important the consensus network is in the whole pipeline
  The low L1 distances show us that not only does the consensus help reconcile the variability in the edges due to multiple network inference algorithms, it also helps reconcile the variability to the other steps of the pipeline as well.
  This result is different from that observed in Figure~\ref{fig:figure2} since in this particular analysis all the steps other than the \ac{ni} step have the consensus algorithm applied to them, which drastically reduces the edges in the graph that have lower probabilities.
  This reinforces the importance of the consensus network in increasing the robustness of the inferred networks to different processing methods.
  Figure~\ref{fig:figure7}C shows the co-occurrence networks inferred for the healthy subjects (control) and autistic subjects in the fecal microbiome transplant study~\cite{Kang2017}.
  These consensus networks were generated using the default tools and parameters from Table~\ref{tab:micone_tools}.

### 2022-05-07 sections/tables_figures.tex
Change: Update the Results for draft v2
Change: Update the tables and figures for draft v2

  \begin{table}[h]

@@

                                                &  & Dada2 & \cite{Callahan2016} \\

@@

                                                & & Remove bimera & \cite{Callahan2016} \\

@@

                                           &  & Naive bayes classifier & \cite{bokulichOptimizingTaxonomicClassification2018} \\

@@

                                           & \multirow{3}{*}{Database} & Greengenes & \cite{DeSantis2006} \\
                                           & & SILVA & \cite{Quast2012} \\
                                           & & NCBI RefSeq & \cite{Sayers2009} \\

@@

                                      & \multirow{3}{*}{Filter(on)}  & Prevalence threshold      & 0.05           \\
                                      & & Abundance threshold       & 0.01           \\
                                      & & Observation sum threshold & 100            \\

@@

      \multirow{12}{*}{Network Inference} & \multirow{2}{*}{Bootstrapping}& \texttt{fastspar\_bootstraps} v1.0 & \cite{Watts2018} \\
                                          & & \texttt{fastspar\_pvalues} v1.0 & \cite{Watts2018} \\

@@

                                          & & propr v2.1.2 & \cite{quinnProprRpackageIdentifying2017} \\

@@

    \caption{Tools used in the \ac{micone} pipeline}

@@

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Workflow step} & \textbf{Default tool} \\
      \hline
      Denoising and Clustering & Dada2 and remove bimera \\
      Taxonomy Assignment & \ac{gg} with NaiveBayes classifier \\
      OTU Processing & Thresholds on prevalence and abundance \\
      Network Inference & scaled-sum consensus method \\
      \hline
    \end{tabular}
    \caption{Default tools and parameters of the \ac{micone} pipeline}
    \label{tab:default_options}
  \end{table}

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.74\linewidth]{figure1.pdf}
  \end{figure}
  \begin{figure}[ht!]
    \centering
    \caption{
      \textbf{The workflow of the \ac{micone} pipeline}.
      The steps can be grouped into five major groups: \textbf{(SP)} \textbf{S}equence \textbf{P}rocessig, \textbf{(DC)} \textbf{D}enoising and \textbf{C}lustering, \textbf{(TA)} \textbf{T}axonomy \textbf{A}ssignment, \textbf{(OP)} \textbf{O}TU or ESV \textbf{P}rocessing, and \textbf{(NI)} \textbf{N}etwork \textbf{I}nference.
      Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
      The text along the arrows describes the data that is being passed from one step to another.
      The final output of the pipeline are consensus networks generated from the co-occurrence networks.
      For details on each process and data types, see Methods.
    }
    \label{fig:figure1}
  \end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\linewidth]{figure2.pdf}
  \end{figure}
  \begin{figure}
    \centering
      \caption{
      \textbf{The choice of reference database contributes to the most variance in the networks}.
      \textbf{(A)} The total relative variance in the networks contributed by the DC, CC (chimera checking), TA and OP steps of the pipeline (right) and the linear model used to calculate the relative variance (left), see the Methods section for details.
      The analyses was performed on the healthy stool samples in a fecal microbiome transplant dataset~\ref{Kang2017}.
      The taxonomy database contributes most to the variance between the networks (65.4\%) followed by filtering of the counts matrix (26.8\%) in the OP step.
      \textbf{(B)} All combinations of inferred networks are shown as points on a PCA plot.
      Each point on the PCA plot represents a network inferred using different combinations of tools and parameters that are available in the \ac{micone} pipeline.
      The color of the points corresponds to the reference taxonomy database used to reconstruct those networks (left), and the network inference algorithm used to infer the networks (right).
      % TODO: The points aren't really separated
      The points on the PCA plot can be separated based on the TA step and the differences due to the DC and CC steps are comparatively not as significant.
    }
    \label{fig:figure2}
  \end{figure}
  \FloatBarrier
  \newpage

  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure3.pdf}
  \end{figure}
  \begin{figure}
    \centering
    \caption{
      \textbf{The representative sequences generated by the different denoising/clustering methods are very similar but differ in the sequences that are lower in abundance.}
      \textbf{(A)} The average weighted UniFrac distance between the representative sequences shows that the representative sequences and their compositions are fairly identical between the methods (with the exception of Deblur (DB)).
      \textbf{(B)} The relatively larger average unweighted UniFrac distance indicates that methods differ in their identification of sequences that are lower in abundance.
      \textbf{(C, D)} The distributions of the average weighted and unweighted UniFrac distance between the expected sequence profile and the calculated sequence profile in the mock datasets.
      The distributions of the average weighted UniFrac distance show that de novo (DN) and open reference (OR) were the best performing methods in most of the datasets, while they are worst performing methods under the unweighted UniFrac metric.
      The above average performance of dada2 (D2) under both distance metrics combined with its approach of identifying \ac{esv}s using de novo methods, prompts us to propose it as the default method for the DC step.
    }
    \label{fig:figure3}
  \end{figure}
  \FloatBarrier
  \newpage

  \begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=1.2\textwidth]{figure4.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{Taxonomic reference databases vary widely in terms of their taxonomy assignments beyond the Order level.}
      \textbf{(A)} The assignments of the top 50 representative sequences to their respective taxonomies using the three different reference databases show how the same sequences are assigned to different Genus under the different databases.
      A significant portion of the representative sequences are assigned to an ``unknown'' Genus in two of three databases (\ac{gg} and \ac{ncbi}).
      \textbf{(B)} The number of representative sequences assigned to the same taxonomic label when using different reference databases, shown for the top 100 sequences.
      The number of mismatches are fewer at higher taxonomic levels but even at the Order level there exists greater than 51\% of mismatches, demonstrating the poor agreement in taxonomic labels assigned by the different databases.
      \textbf{(C)} The Bray-Curtis dissimilarity between the expected taxonomy profile and calculated taxonomy profile in the mock datasets shows that there is no singular best choice of database for every dataset, as all the databases have similar performance.
      However, we recommend the \ac{gg} database due to its popularity and if the goal is to compare against existing networks in literature.
    }
    \label{fig:figure4}
  \end{figure}
  \FloatBarrier
  \newpage

  \begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figure5.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{Networks generated using different network inference methods show notable differences both in terms of edge-density and connectivity}.
      \textbf{(A)} The nine different networks generated by the different network inference methods (excluding \ac{mldm}) are very dissimilar.
      The green links are positive associations and the orange links are negative associations.
      A threshold of 0.3 was set for the correlation-based methods (\ac{sparcc}, Propr, Spearman and Pearson) and a threshold of 0.01 was set for the other direct association methods.
      \textbf{(B)} The node overlap Upset plot indicates that all the networks have a large number of common nodes involved in connections (33 out of 68).
      Whereas, \textbf{(C)} the edge overlap Upset plot shows that a very small fraction of these connections are actually shared (8 out of 202).
    }
    \label{fig:figure5}
  \end{figure}
  \FloatBarrier
  \newpage

  \begin{figure}[h]
    \centering
    \includegraphics[width=1.0\linewidth]{figure6.pdf}
    \caption{
      \textbf{The precision and sensitivity of the inferred networks on the NorTA synthetic interaction data.}
      The ``I'' prefix indicates the individual network inference methods and the ``X'' prefix denotes the different consensus based methods.
      The different consensus based methods used are: pvalue merging (PM), scaled-sum (SS) and simple voting (SV) method.
      Pearson and Spearman methods are not used in the calculation of the consensus.
      Among all the independent network inference methods, \ac{spieceasi} has the best average precision (0.944), but the overall best precision was consistently obtained by the scaled-sum method (0.956, 0.985 and 1.000).
      The simple voting method when using presence of edges in all inferred networks as a requirement (parameter value 1.000), also outperforms \ac{spieceasi} on average precision (0.969).
      Therefore, we recommend the scaled-sum consensus method as the default tool for network inference.
    }
    \label{fig:figure6}
  \end{figure}
  \FloatBarrier
  \newpage

  % TODO: Verify the validity of Figure 7A and 7B again
  % Are they both using consensus?
  \begin{figure}[H]
    \centering
    \includegraphics[width=1.0\linewidth]{figure7.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{The consensus algorithm drastically reduces variability in the networks and increases robustness of inferred networks}
      \textbf{(A)} The network constructed using the default pipeline parameters (DC=\ac{dada2}, CC=remove bimera, TA=\ac{gg}, OP=Filter(on), NI=scaled-sum consensus) is compared with networks generated when one of the steps use a different tool.
      The common connections (common with the default network) are in black, connections unique to the network are colored purple and connections in the default network but not present in the current network are gray.
      Changing the NI, TA and OP steps leads to the creation of the most number of new nodes and edges.
      \textbf{(B)} The boxplot showing the L1 distance between the networks generated by changing one step of the default pipeline and the network generated using the default parameters.
      The high value of L1 distances for the network inference step as compared to the other steps demonstrates how the consensus method is able to reduce the variability in the networks in the other steps of the pipeline.
      \textbf{(C)} The networks generated for the control (left) and autistic (right) samples in the fecal microbiome transplant dataset.
      These networks were generated using the default tools and parameters recommended by the \ac{micone} pipeline.
    }
    \label{fig:figure7}
  \end{figure}

>>>>

  \begin{table}[H]

@@

                                                &  & \rowcolor{lightgray} Dada2 & \cite{Callahan2016} \\

@@

                                                & & \rowcolor{lightgray} Remove bimera & \cite{Callahan2016} \\

@@

                                           &  & \rowcolor{lightgray} Naive bayes classifier & \cite{bokulichOptimizingTaxonomicClassification2018} \\

@@

                                           & \multirow{3}{*}{Database} & \rowcolor{lightgray} Greengenes 13\_8 & \cite{DeSantis2006} \\
                                           & & SILVA 138 & \cite{Quast2012} \\
                                           & & NCBI RefSeq (Oct 2021) & \cite{Sayers2009} \\

@@

                                      & \multirow{3}{*}{Filter(on)}  & \rowcolor{lightgray} Prevalence threshold      & 0.05           \\
                                      & & \rowcolor{lightgray} Abundance threshold       & 0.01           \\
                                      & & \rowcolor{lightgray} Observation sum threshold & 100            \\

@@

      \multirow{12}{*}{Network Inference} & \multirow{2}{*}{Bootstrapping}& fastspar\_bootstraps v1.0 & \cite{Watts2018} \\
                                          & & fastspar\_pvalues v1.0 & \cite{Watts2018} \\

@@

                                          & & propr v2.1.2 & \cite{quinnProprRpackageIdentifying2017} \\ \cline{2-4}
                                          & \multirow{2}{*}{Consensus algorithm} & \rowcolor{lightgray} scaled-sum & 0.667 \\
                                          & & simple voting & 0.667 \\

@@

    \caption{
      \textbf{Tools used in the \ac{micone} pipeline}.
      The tools highlighted in gray are the defaults for the pipeline and are recommended based on the benchmarks with the mock and synthetic datasets.
      The consensus algorithm in the \ac{ni} step incorporates all the modules (bootstrapping, direct association and correlation-based) in that step to generate the consensus network.
    }

@@

@@

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.74\linewidth]{figure1.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{The workflow of the \ac{micone} pipeline}.
      The steps of the workflow can be broken down into five major groups: \textbf{(SP)} \textbf{S}equence \textbf{P}rocessig, \textbf{(DC)} \textbf{D}enoising and \textbf{C}lustering, \textbf{(TA)} \textbf{T}axonomy \textbf{A}ssignment, \textbf{(OP)} \textbf{O}TU and ESV \textbf{P}rocessing, and \textbf{(NI)} \textbf{N}etwork \textbf{I}nference.
      Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
      The text along the arrows describes the data that is being passed from one step to another.
      The final output of the pipeline is the consensus network generated from the inferred co-occurrence networks.
      For details on each process and the data outputs, see Methods.
    }
    \label{fig:figure1}
  \end{figure}

@@

  % TODO: Add equations for the linear model to the left of the pie chart
  \begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figure2.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
      \caption{
      \textbf{The choice of reference database contributes to the most variance in the networks}.
      \textbf{(A)} The percentage of variance in the networks contributed by the DC, CC (chimera checking), TA and OP steps of the pipeline (right) and the linear model used to calculate the variance (left), see the Methods section for details.
      The data used for the analysis were the healthy stool samples from the fecal microbiome transplant dataset~\ref{Kang2017}.
      The taxonomy database contributes most to the variance between the networks (65.4\%) followed by the filtering of the counts matrix (26.8\%) in the OP step.
      The variation due to the DC and CC steps are comparatively not as significant.
      \textbf{(B)} All combinations of inferred networks are shown as points on a PCA plot.
      Each point on the PCA plot represents a network inferred using different combinations of tools and parameters that are available in the \ac{micone} pipeline.
      The color of the points corresponds to the reference taxonomy database used to reconstruct those networks (left), and the network inference algorithm used to infer the networks (right).
      The points on the PCA plot can be grouped based on the TA step, but at the NI step only some methods create high variability in the inferred networks.
    }
    \label{fig:figure2}
  \end{figure}
  \FloatBarrier
  \newpage

  \begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figure3.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{The representative sequences generated by the different denoising/clustering methods are very similar but differ in the sequences that are lower in abundance.}
      \textbf{(A)} The average weighted UniFrac distance between the representative sequences shows that the representative sequences and their compositions are fairly identical between the methods (with the exception of Deblur (DB)).
      \textbf{(B)} The relatively larger average unweighted UniFrac distance indicates that methods differ in their identification of sequences that are lower in abundance.
      The number of \ac{otu}s or \ac{esv}s generated by the respective methods are provided in the parenthesis next to the names.
      \textbf{(C, D)} The distributions of the average weighted and unweighted UniFrac distance between the expected sequence profile and the predicted sequence profile in the mock datasets.
      The distributions of the average weighted UniFrac distance show that de novo (DN) and open reference (OR) were the best performing methods in most of the datasets, while they are worst performing methods under the unweighted UniFrac metric.
      The good performance of dada2 (D2) under both distance metrics combined with its approach of identifying \ac{esv}s using de novo methods, prompts us to propose it as the default method for the DC step.
    }
    \label{fig:figure3}
  \end{figure}
  \FloatBarrier
  \newpage

  \begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=1.2\textwidth]{figure4.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{Taxonomic reference databases vary widely in terms of their taxonomy assignments beyond the Order level.}
      \textbf{(A)} The assignments of the top 50 representative sequences to their respective taxonomies using the three different reference databases.
      This result clearly describes how the same sequences are assigned to different Genus under the different databases.
      A significant portion of the representative sequences are assigned to an ``unknown'' Genus in two of three databases (\ac{gg} and \ac{ncbi}).
      \textbf{(B)} The number of representative sequences assigned to the same taxonomic label when using different reference databases, shown for the top 100 sequences.
      The number of mismatches are fewer at higher taxonomic levels, but, even at the Order level there exists greater than 51\% of mismatches, demonstrating the poor agreement in taxonomic labels assigned by the different databases.
      \textbf{(C)} The Bray-Curtis dissimilarity between the expected taxonomy profile and calculated taxonomy profile in the mock datasets shows that there is no singular best choice of database for every dataset, as all the databases have similar performance.
      However, we still recommend the \ac{gg} database and the Naive Bayes classifier as the defaults for the \ac{micone} pipeline.
      Due to the popularity of the \ac{gg} database, comparison against existing networks in literature will be easier since many published datasets make use of this database in their analyses.
    }
    \label{fig:figure4}
  \end{figure}
  \FloatBarrier
  \newpage

  \begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figure5.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{Networks generated using different network inference methods show notable differences both in terms of edge-density and connectivity}.
      \textbf{(A)} The nine different networks (excluding \ac{mldm}) generated by the different network inference methods are very dissimilar.
      The green links are positive associations and the orange links represent negative associations.
      A threshold of 0.3 was set for the correlation-based methods (\ac{sparcc}, Propr, Spearman and Pearson) and a threshold of 0.01 was set for the other direct association methods.
      The correlation-based methods in general produce graph with higher edge-densities.
      \textbf{(B)} The node overlap Upset plot indicates that all the networks have a large proportion of common nodes involved in connections (33 out of 68).
      Whereas, \textbf{(C)} the edge overlap Upset plot shows that a very small fraction of these connections are actually shared (8 out of 202).
    }
    \label{fig:figure5}
  \end{figure}
  \FloatBarrier
  \newpage

  \begin{figure}[H]
    \centering
    \includegraphics[width=1.0\linewidth]{figure6.pdf}
    \caption{
      \textbf{The precision and sensitivity of the inferred networks on the NorTA synthetic interaction data.}
      The ``I'' prefix indicates the individual network inference methods and the ``X'' prefix denotes the consensus based methods that are a part of \ac{micone}.
      The different consensus based methods used are: pvalue merging (PM), scaled-sum (SS) and simple voting (SV) method.
      Pearson and Spearman methods are not used in the calculation of the consensus.
      Among all the independent network inference methods, \ac{spieceasi} has the best average precision (0.944), but the overall best precision was consistently obtained by the scaled-sum method (0.956, 0.985 and 1.000).
      The simple voting method when using presence of edges in all inferred networks as a requirement (parameter value 1.000), also outperforms \ac{spieceasi} on average precision (0.969).
      Although \ac{spieceasi} has a higher performance on sensitivity, if the goal of network inference is to obtain the list of associations that have a high probability of existing in the real microbial community, then the consensus methods perform better.
      Therefore, we recommend the scaled-sum consensus method as the default tool for network inference.
    }
    \label{fig:figure6}
  \end{figure}
  \FloatBarrier
  \newpage

  % TODO: Verify the validity of Figure 7A and 7B again
  % Are they both using consensus?
  \begin{figure}[H]
    \centering
    \includegraphics[width=1.0\linewidth]{figure7.pdf}
  \end{figure}
  \begin{figure}[H]
    \centering
    \caption{
      \textbf{The consensus algorithm drastically reduces variability in the networks due to upstream data processing methods and increases robustness of inferred networks}
      \textbf{(A)} The network constructed using the default pipeline parameters (DC=\ac{dada2}, CC=remove bimera, TA=\ac{gg}, OP=Filter(on), NI=scaled-sum consensus) is compared with networks generated when one of the steps use a different tool.
      The common connections (common with the default network) are in black, connections unique to the network are colored purple and connections in the default network, but not present in the current network are gray.
      Changing the NI, TA and OP steps leads to the creation of the most number of new nodes and edges.
      \textbf{(B)} The boxplot showing the L1 distance between the default network and the networks generated by changing one step of the default pipeline.
      The high value of L1 distances for the network inference step as compared to the other steps demonstrates how the consensus method is able to reduce the variability in the networks in the other steps of the pipeline.
      This also shows that even though many new nodes were added in (A) when the TA and OP steps were changed, the L1 distances remain fairly small.
      \textbf{(C)} The networks generated for the control (left) and autistic (right) samples in the fecal microbiome transplant dataset.
      These networks were generated using the default tools and parameters recommended by the \ac{micone} pipeline.
    }
    \label{fig:figure7}
  \end{figure}
